Article Title

### 2020-06-19 paper/article_2.tex
updates

\section{Introduction}
In the last years, the precision of the Planck experiment [cita], whose task was to analyse the Cosmic Microwave Background (CMB) anisotropies, has allowed to fully test our standard cosmological model $\Lambda$CDM which assumes the existence of Dark Energy ($\Lambda$) and Cold Dark Matter (CDM). In particular, in addition to the minimal 6 parameters describing $\Lambda$CDM, the CMB anisotropies allow to indirectly constrain other parameters, such as the current expansion rate of the Universe, $H_0$, whose inference strongly depends on the assumed cosmological model. For example, relaxing the spatial flatness hypothesis of our Universe or the constant equation of state for the dark energy, would change the estimated value of $H_0$.
\\
In parallel, the are other independent methods to measure $H_0$, such as the distance ladder [cita], water masers [cita], the time delay between multiple images of gravitational lensed quasars [cita H0LiCOW] and, gravitational waves [cita].
\\
In this paper we will focus on the gravitational lensing: firstly suggested by Refsdal \cite{refsdal}, this method directly relates the time delays between multiple images of the same source produced by a lensing object with $H_0$ in the form $\Delta_T \propto 1/H_0$. This method depends on the matter distribution of both the lensing object (such as a galaxy) and along the line of sight, and it has a weaker dependence on the cosmological parameters if compared to the CMB analyses. In particular, it depends on the matter density $\Omega_m$, the dark energy density $\Omega_\Lambda$, the curvature parameter $\Omega_k$ and the dark energy equation of state $\omega$ [cita].
\\
This method requires a long (of the order of years) photometric monitoring of the multiple images of the source and a good temporal sampling, to be able to observe the photometric variations of the source. In this regard, the COSMOGRAIL collaboration has been monitoring 18 strongly lensed quasars since 2004 \cite{cosmograil}. And the H0LiCOW collaboration has used part of these data to evaluate $H_0$ with a precision of $2.4\%$ \cite{h0licow_XIII}.

>>>>

\section{Introduction}
In the last years, the precision of the Planck experiment [cita], whose task was to analyse the Cosmic Microwave Background (CMB) anisotropies, has allowed to fully test our standard cosmological model $\Lambda$CDM which assumes the existence of Dark Energy ($\Lambda$) and Cold Dark Matter (CDM). In particular, in addition to the minimal 6 parameters describing $\Lambda$CDM, the CMB anisotropies allow to indirectly constrain other parameters, such as the current expansion rate of the Universe, $H_0$, whose inference strongly depends on the assumed cosmological model. For example, relaxing the spatial flatness hypothesis of our Universe or the constant equation of state for the dark energy, would change the estimated value of $H_0$.
\\
In parallel, the are other independent methods to measure $H_0$, such as the distance ladder [cita], water masers [cita], the time delay between multiple images of gravitational lensed quasars [cita H0LiCOW] and, gravitational waves [cita]. The highest precision reached by Plank has however shown a tension in the value of $H_0$ with respect to the distance ladder measurement. This tension has been further enhanced by the recent gravitational lensing results from the H0LiCOW collaboration, which agree with the distance ladder measured value of  $H_0$ and brings to a $5.7 \sigma$ tension with the CMB result.
\\
In this paper we will focus on the gravitational lensing: firstly suggested by Refsdal \cite{refsdal}, this method directly relates the time delays between multiple images of the same source produced by a lensing object with $H_0$ in the form $\Delta_T \propto 1/H_0$. This method depends on the matter distribution of both the lensing object (such as a galaxy) and along the line of sight, and it has a weaker dependence on the cosmological parameters if compared to the CMB analyses. In particular, it depends on the matter density $\Omega_m$, the dark energy density $\Omega_\Lambda$, the curvature parameter $\Omega_k$ and the dark energy equation of state $\omega$ [cita].
\\
This method requires a long (of the order of years) photometric monitoring of the multiple images of the source and a good temporal sampling, to be able to observe the photometric variations of the source. In this regard, the COSMOGRAIL collaboration has been monitoring 18 strongly lensed quasars since 2004 \cite{cosmograil} with 1-2 m size telescopes. And the H0LiCOW collaboration has used part of these data to evaluate $H_0$ with a precision of $2.4\%$ \cite{h0licow_XIII}. 
\\
